
\documentclass[a4paper,20pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=black,
}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage{natbib}
\usepackage{bibentry}
\nobibliography{resume.bib}
% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}


%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://officialadithya.github.io}{\LARGE ADITHYA BHASKARA}} & \textit{References available upon request.} \\
  Boulder, CO & \href{mailto:adithya@colorado.edu}{adithya@colorado.edu}\\
  \href{https://www.linkedin.com/in/adithya-bhaskara/}{linkedin.com/in/adithya-bhaskara/} & +1 (720) 600-9029 \\ & \href{https://scholar.google.com/citations?user=lO0J2oMAAAAJ}{Google Scholar}
\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.colorado.edu}{University of Colorado Boulder}}{Boulder, Colorado}
      {Bachelor of Science - Computer Science; Bachelor of Arts - Mathematics}{August, 2022 - May, 2026}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Data Structures, Linear Algebra, Algorithms, Theory of Computation, Computational Complexity, Linear and Integer Programming, Quantum Computing, Computer Systems, Principles of Programming Languages (In Progress), Real Analysis I, Abstract Algebra I}}}
      {\scriptsize \textit{\footnotesize{\newline{}\textbf{Major GPA:} 4.000, \textbf{Cumulative GPA:} 3.986 }}}
    \resumeSubheading
      {\href{https://www.frontrange.edu}{Front Range Community College}}{Longmont, Colorado}
      {High School Concurrent Enrollment}{June, 2021 - August, 2022}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Calculus III, Differential Equations With Linear Algebra, Discrete Mathematics, Physics I, Physics II, Introduction to C++}}}
      {\scriptsize \textit{\footnotesize{\newline{}\textbf{Cumulative GPA:} 4.000 }}}
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}
\section{Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Computer Languages \& Tools}{~~~~~~Python, C++, Java*, Matlab*, Scala* \LaTeX, Docker*, HTML*, CSS*, JavaScript*}
    \resumeSubItem{Human Languages}{~~~~~~~~~~~~~~~~~~~~~~~English, Kannada, French*}
	\resumeSubItem{Soft Skills}{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~Teaching, Leadership, Communication} \\\vspace{8pt}
    * \textit{Elementary Proficiency}
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading{University of Colorado Boulder}{Boulder, CO}
    {Theoretical Computer Science Undergraduate Researcher, Advised by Rafael Frongillo, Ph. D.}{May, 2023 - Present}

    \begin{itemize}
        \itemsep -1pt {}
        \item Sought to understand optimal liquidity provisioning in decentralized exchanges and prediction markets.
        \item Sought to understand aspects of liquidity provisioning from a contract design perspective and formulated a general theory for automated market makers, resulting in the paper:
        \begin{itemize}
          \item \bibentry{bhaskara2023general}
        \end{itemize}
        \item Developed basic understanding of topics in algorithmic game theory and computational social choice theory.
        \item Active in the algorithmic economics reading group.
    \end{itemize}
    \resumeSubheading{University of Colorado Boulder}{Boulder, CO}
    {CSCI 3104: Algorithms Learning Assistant}{January, 2024 - May, 2024}

    \begin{itemize}
        \itemsep -1pt {}
        \item Met regularly with the Algorithms instructional team to prepare for the upcoming week of instruction and ensure student success.
        \item Held regular office hours to help students with fundamental algorithms concepts including graph algorithms, the divide-and-conquer paradigm, dynamic programming, amortized analysis, and computational complexity theory.
        \item Served as a resource for students to voice questions and concerns about Calculus I content.
    \end{itemize}
  \resumeSubheading{University of Colorado Boulder}{Boulder, CO}
    {MATH 1300: Calculus I Learning Assistant}{January, 2023 - May, 2023}

    \begin{itemize}
        \itemsep -1pt {}
        \item Co-led two weekly recitation sections of \(\approx 35\) students each for Calculus I with a graduate teaching assistant.
        \item Met regularly with the Calculus I instructional team to prepare for the upcoming week of instruction and ensure student success.
        \item Tutored students in the University of Colorado Boulder's Mathematics Academic Resource Center help room.
        \item Served as a resource for students to voice questions and concerns about Calculus I content.
    \end{itemize}
%     \resumeSubheading{St. Vrain Valley Schools Innovation Center}{Longmont, CO}
%     {Founding Member of the Cybersecurity Student Project Team}{August, 2019 - July, 2022}

%     \begin{itemize}
%         \itemsep -1pt {}
%         \item Spearheaded effort to create middle school computer programming competition.
%             \begin{itemize}
%                 \item Served as competition administrator and lead problem author. Oversaw development of \(\approx 80\) problems.
%                 \item Fielded \(13\) teams of \(2\) to \(4\) students per team in inaugural year.
%             \end{itemize}
%         \item Organized St. Vrain Valley Schools' participation, and competed, in the National CyberPatriot Competition (\(\approx 30\) competitors).
%             \begin{itemize}
%                 \item Led practices and presented on topics in Linux system administration.
%                 \item Led own team to platinum tier of competition and semifinal rounds multiple times.
%             \end{itemize}
%         \item Taught introductory cybersecurity classes of \(\approx 25\) students and developed instructional materials; trained coworkers.
%         \item Regularly presented to district and community leaders, including Governor Jared Polis, during board meetings and Innovation Center tours.
%     \end{itemize}
 \vspace{-5pt}
    % \resumeSubheading
		% {Silver Creek High School}{Longmont, CO}
		% {Instructional Student Assistant Program Director}{August, 2021 -  May, 2022}
		% \begin{itemize}
    %         \itemsep -1pt {}
    %         \item Served as head teaching assistant.
    %         \item Created lessons and miscellaneous instructional materials, assisted students, and gave lectures for Algebra I, Algebra II, and Introductory Physics.
    %         \item Oversaw \(7\) teaching assistants in Prealgebra, Geometry, Integrated English and History, United States History, and Personal Finance. Led monthly professional development meetings.
    %     \end{itemize}

\resumeSubHeadingListEnd
\vspace{-5pt}
\section{Honors, Awards, and Funding}
\begin{description}[font=$\bullet$]
\item {\href{https://boettcherfoundation.org}{Boettcher Scholarship (Full Ride \(\approx\$140,000\) Value) Awardee \hfill \textit{April, 2022}}}
\vspace{-5pt}
\item {\href{https://www.colorado.edu/cs-theory/alg-econ}{Algorithmic Economics NSF REU Grant (\(\approx\$8,000\) Value) Recipient\hfill \textit{May, 2023}}}
\begin{itemize}
  \item \footnotesize{Funded by Rafael Frongillo's NSF CAREER Award.}
\end{itemize}
\vspace{-5pt}
\item {Marlene Massaro Pratto and David Pratto Scholarship in Mathematics (\(\$2,500\) Value) \hfill \textit{June, 2024}}
\vspace{-5pt}
\item {\href{https://cuengineeringhonors.com}{University of Colorado Boulder Engineering Honors Student \hfill \textit{February, 2022}}}
\vspace{-5pt}
\item {\href{https://www.nationalmerit.org}{National Merit Finalist \hfill \textit{February, 2022}}}
\vspace{-5pt}
\item {Colorado School of Mines Medal of Achievement in Mathematics and Science Awardee \hfill \textit{May, 2021}}
\end{description}

\section{Scholarly Service \& Additional Research Activity}
\begin{description}[font=$\bullet$]
\item Engineering Honors Program Admissions Executive Committee Member \hfill \textit{University of Colorado Boulder, 2024}
\vspace{-5pt}
\item \href{https://www.colorado.edu/boettcher-daniels-norlin-scholars/norlin-scholars}{Norlin Scholarship Admissions Reviewer} \hfill \textit{University of Colorado Boulder, 2023, 2024}
\end{description}

\begin{comment}
%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Vison - multimedia search engine (NLP, Search Engine, Web Crawlers, Multimedia Processing)}{(Work in progress) Research oriented, open source, search engine for bringing reverse multimedia search to small \& mid scale enterprises. Tech: Python, NodeJS, Intel OpenVino Toolkit, Selenium, TensorFlow (October '18)}
\vspace{2pt}
\resumeSubItem{Reinforcement Learning based Traffic Control System (Reinforcement Learning, Computer Vision)}{AI model to resolve city traffic around 50\%
faster. Tech: Python, Alibaba Cloud, Raspberry Pi, Arduino, SUMO \& OpenCV. (August '18)}
\vspace{2pt}
\resumeSubItem{Panorama from Satellite Imagery using Distributed Computing (Distributed Computing, Image Processing)}{Images clicked using drones, provided by ISRO were stitched together using distributed public compute nodes, effectively bringing down processing time exponentially. Tech: PHP, C++, Java, Python (March '18)}
\vspace{2pt}
\resumeSubItem{Drag-n-drop machine learning learning environment (Web Development, Machine Learning)}{Scratch like tool for implementing machine learning pipelines along with built in tutorial for each concept. Tech: Python, JavaScript (September '18)}
\vspace{2pt}
\resumeSubItem{Search Engine and Social Network(Web Development, Web Crawler, Search)}{Created from scratch a social network and a search engine based on the idea of integrating Facebook and Google. The launched website was among top 1000 websites in India during 2012-2013. Tech: PHP, MySQL, HTML, CSS, WebSockets, JavaScript, RSS, XML ( May '12)}
\resumeSubHeadingListEnd
\vspace{-5pt}
\section{Publications}
\resumeSubHeadingListStart
\resumeSubItem{Book: Deep Learning on Web (Web Development, Deep Learning)}{Work in Progress book to be published by Packt Publishing in late 2019. Tech: Django, Python, AWS, GCP, Azure (November '18)}
\vspace{2pt}
\resumeSubItem{Book: Deep Learning on Mobile Devices (Flutter App Development, Deep Learning)}{Work in Progress book to be published by Packt Publishing in late 2019. Tech: Flutter, Android, Firebase, TensorFlow, Python, Dart (December '18)}
\resumeSubHeadingListEnd
\vspace{-5pt}
%-----------Awards-----------------
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
\item {Awarded title of Intel Software Innovator - May, 2019}
\vspace{-5pt}
\item {Second Runner's Up at TCS EngiNx Engineering Project Innovation Content - September, 2018 }
\vspace{-5pt}
\item {Runner's Up at Facebook Developers Circle Hackathon - August, 2017}

\end{description}

\vspace{-5pt}
\section{Volunteer Experience}
  \resumeSubHeadingListStart
	\resumeSubheading
    {Community Lead at Developer Student Clubs NSEC}{Kolkata, India}
    {Conducted online and offline technical \& soft-skills training impacting over 3000 students.}{Jan 2019 - Present}
\vspace{5pt}
    % \vspace{10pt}\textbf{\large{Community Experience}}
    \resumeSubheading
    {Event Organizer at Google Developers Group Kolkata}{Kolkata, India}
    {Organized events, conducted workshops and delivered workshops reaching over 7000 developers.}{Jan 2018 - Present}

\resumeSubHeadingListEnd
\end{comment}
\pagebreak
\bibliographystyle{plain}
\bibliography{resume.bib}
\end{document}
