\documentclass[a4paper,20pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage{natbib}
\usepackage{bibentry}
\nobibliography{resume.bib}
% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}


%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\LARGE ADITHYA BHASKARA} & \textit{References available upon request.} \\
  Boulder, CO & \href{mailto:adithya@colorado.edu}{adithya@colorado.edu}\\
  \href{https://officialadithya.github.io}{officialadithya.github.io} & +1 (720) 600-9029 \\ \href{http://adithyacolorado.bsky.social}{@adithyacolorado.bsky.social} & \href{https://scholar.google.com/citations?user=lO0J2oMAAAAJ}{Google Scholar}
\end{tabular*}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Colorado Boulder}{Boulder, Colorado}
      {B.S. Computer Science; B.A. Mathematics}{August, 2022 - May, 2026 (Expected)}
      \\
      {\scriptsize \textit{\footnotesize{\newline{}\textbf{Major GPA:} 4.000, \textbf{Cumulative GPA:} 3.991 (as of May. 2025) \href{https://officialadithya.github.io/assets/pdf/resume/unofficial_transcript.pdf}{Transcript}.}}}
      \\
      \vspace{3pt}
      {\small \textbf{Thesis Work:} Tradeoffs Between Randomness, Robust Alternate Selection, and Other Desiderata for Sortition (Title TBD) \\
      \vspace{-5pt}
      \begin{enumerate} \item[] \hfill{Advised by \href{https://sites.google.com/mit.edu/bailey-flanigan/home}{Bailey Flanigan, Ph. D.} (MIT) and \href{https://raf.prof}{Rafael Frongillo, Ph. D.}} \end{enumerate}}
      \vspace{-20pt}
      {\scriptsize \textit{\footnotesize{\newline{}\textbf{Relevant Coursework:} 8 Graduate Courses Including Linear and Integer Programming, Algebra 1, Theory of Computation, Design and Analysis of Algorithms, Advanced Algorithms, Algorithmic Economics, Advanced Convex Optimization, Measure-Theoretic Probability (In Progress), Complexity Theory (Audit)}}}
            % \resumeSubheading
    %   {Front Range Community College}{Longmont, Colorado}
    %   {High School Concurrent Enrollment}{June, 2021 - August, 2022}
    %   \\
    %   {\scriptsize \textit{\footnotesize{\newline{}\textbf{Cumulative GPA:} 4.000 }}}
    \resumeSubHeadingListEnd

    \vspace{-5pt}
    \section{Research Experience}
    \textbf{University of Colorado Boulder \hfill{Undergraduate Researcher}} \\
    Research interests include topics in (broadly) theoretical computer science, especially computational social choice theory, algorithmic economics, matrix mltiplication, and (fine-grained) complexity theory.
    \\
    \emph{Advised by \href{https://sites.google.com/mit.edu/bailey-flanigan/home}{Bailey Flanigan, Ph. D.}}\hfill{\textit{August, 2023 - Present}}
    \\
    \begin{itemize}[label=-]
      \vspace{-5pt}
      \item Studying the tradeoffs between randomness and other desiderata for sortition algorithms.
      \vspace{-5pt}
      \item Proving integrality gaps and other theoretical results for an associated convex optimization problem. 
      \vspace{-5pt}
      \item Interested in how to select alternate panelists robust to agents' misreports of their features.
      \vspace{-5pt}
      \item Attended Social Choice: Theory and Computation, An Interdisciplinary Conference on Voting, Representation, and Districting
    \end{itemize}
    \emph{Advised by \href{https://raf.prof}{Rafael Frongillo, Ph. D.}}\hfill{\textit{May, 2023 - Present}}
    \\
    \begin{itemize}[label=-]
      \vspace{-5pt}
      \item Seeking to understand and characterize the design spaces of liquidity provisioning and transaction fee protocols in prediction markets and decentralized exchanges.
      \vspace{-5pt}
      \item Captured liquidity provisioning as several automated market makers operating in parallel and resulting implications.
      \vspace{-5pt}
      \item Assisted Rafael Frongillo with reviewing two submissions to SODA'25 and Management Science (2023).
      \vspace{-5pt}
      \item Regular attendee and presenter in the algorithmic economics reading group.
      \vspace{-5pt}
      \item Attended EC'24, EC'25.
   \end{itemize}
   \emph{Advised by \href{https://home.cs.colorado.edu/~hbennett/}{Huck Bennett, Ph. D.}}\hfill{\textit{February, 2025 - Present}}
   \\
    \begin{itemize}[label=-]
      \vspace{-5pt}
      \item Sought to develop algorithms for special cases of the \textsc{MatrixMultiplicationVerification} problem using Lee metric codes, rank metric codes, and other techniques from coding theory. 
      \vspace{-5pt}
      \item Hoped to take advantage of the structure of the matrices to create better algorithms; project joint with \href{https://www.noahsd.com}{Noah Stephens-Davidowitz, Ph. D.} (Cornell).
      \vspace{-5pt}
      \item Surveying the fine-grained complexity of linear algebraic problems by studying fine-grained reductions.
      \vspace{-5pt}
      \item Attended STOC'25
   \end{itemize} 
   \textsc{Preprints}
   \begin{enumerate}
    \item \bibentry{bhaskara2025general}
  \end{enumerate}
  \textsc{Talks}
  \begin{enumerate}
    \item \bibentry{bhaskara2024generalecdefitalk}, \href{https://www.youtube.com/watch?v=JWsXMNSOygA}{Recording}.
  \end{enumerate}
  \section{Honors and Awards}
  \begin{description}[font=$\bullet$]
  % \vspace{-5pt}
  % \item {\href{https://ec24.sigecom.org/index.html}{Economics and Computation} 2024 Travel Grant, Funded by Rafael Frongillo's NSF CAREER Award \hfill \textit{July, 2024}}
  % \vspace{-5pt}
  % \item {\href{https://www.colorado.edu/cs-theory/alg-econ}{Algorithmic Economics} NSF REU Grant Recipient, Funded by Rafael Frongillo's NSF CAREER Award \hfill \textit{May, 2023}}
  % \begin{itemize}
  %   \item \footnotesize{Funded by Rafael Frongillo's NSF CAREER Award.}
  % \end{itemize}
  \item Endorsed by the University of Colorado Boulder as a candidate for the \href{https://www.churchillscholarship.org}{Churchill Scholarship} \hfill \textit{September, 2025}
  \vspace{-5pt}
  \item Admitted to \href{https://cmmrs.mpi-sws.org}{The Cornell, Maryland, Max Planck Pre-doctoral Research School in Computer Science} \hfill \textit{March, 2025}
  \vspace{-5pt}
  \item Awarded a Boettcher Foundation Educational Enrichment Grant to Attend \href{https://acm-stoc.org/stoc2025/}{STOC'25} \hfill \textit{March, 2025}
  \vspace{-5pt}
  \item {Awarded the Marlene Massaro Pratto and David Pratto Scholarship in Mathematics \hfill \textit{June, 2024}}
  \vspace{-5pt}
  \item {Awarded the \href{https://scholarshipamerica.org/scholarship/westerndigital-wecare/}{Western Digital We.care Scholarship} (Declined) \hfill \textit{May, 2022}}
  \vspace{-5pt}
  \item {Awarded the \href{https://boettcherfoundation.org}{Boettcher Scholarship} (Undergraduate Merit-Based Full Ride) \hfill \textit{April, 2022}}
  \vspace{-5pt}
  \item {University of Colorado Boulder \href{https://cuengineeringhonors.com}{Engineering Honors} Student \hfill \textit{February, 2022}}
  \vspace{-5pt}
  \item {Recognized as a \href{https://www.nationalmerit.org}{National Merit Finalist} \hfill \textit{February, 2022}}
  \vspace{-5pt}
  \item {Awarded the Horace M. Hale Esteemed Scholarship \hfill \textit{January, 2022}}
  \vspace{-5pt}
  \item {Awarded the Colorado School of Mines Medal of Achievement in Mathematics and Science \hfill \textit{May, 2021}}
  \end{description}
  \section{Scholarly Service \& Additional Research Activity}
    \begin{description}[font=$\bullet$]
    \item Engineering Honors Program Admissions Reviewer \hfill \textit{University of Colorado Boulder, 2024, 2025}
    \vspace{-5pt}
    \begin{itemize}[label=-]
      \item Executive Committee Member \hspace{\fill} \textit{2024}
    \end{itemize}
    \vspace{-10pt}
    \item \href{https://www.colorado.edu/boettcher-daniels-norlin-scholars/norlin-scholars}{Norlin Scholarship} Admissions Reviewer \hfill \textit{University of Colorado Boulder, 2023, 2024, 2025}
    \vspace{-5pt}
    \item Boettcher Scholarship Recruitment \& Alumni Ambassador \hfill \textit{Boettcher Foundation, 2025}
    \vspace{-5pt}
    \item Engineering Honors Program First-Year Seminar Recitation Leader \hfill \textit{University of Colorado Boulder, 2024}
    \vspace{-5pt}
    \item Semi-technical blog on topics in mathematics and theoretical computer science at \href{https://officialadithya.github.io/blog/}{https://officialadithya.github.io/blog/}
    \vspace{-5pt}
    \end{description}
    \section{Teaching Experience}
      \textbf{University of Colorado Boulder}
      \begin{itemize}
        \vspace{-5pt}
        \item CSCI 3104: Algorithms, Spring 2024, Fall 2025. Course Assistant.
        \vspace{-5pt}
        \item CSCI 3155: Principles of Programming Languages, Spring 2025. Course Assistant.
        \vspace{-5pt}
        \item MATH 1300: Calculus I, Spring 2023. Learning Assistant.
        \vspace{-5pt}
        \item Scribed \href{https://officialadithya.github.io/assets/pdf/course_materials/linearalgebra.pdf}{course notes} while taking MATH 2135: Linear Algebra for Mathematics Majors in Fall 2022.
        \vspace{-5pt}
      \end{itemize}
      \textbf{Silver Creek High School}
      \begin{itemize}
          \vspace{-5pt}
          \item Instructional Student Assistant (ISA) Program Director, Fall 2021-Spring 2022. Oversaw 7 ISAs.
          \vspace{-5pt}
          \item College-Preparatory Physics, Spring, Fall 2021-Spring 2022. Instructional Student Assistant. 
          \vspace{-5pt}
          \item High School Algebra I, Fall 2020. Instructional Student Assistant. 
          \vspace{-5pt}
          \item High School Algebra II, Spring 2020. Instructional Student Assistant.
          \vspace{-5pt}
        \end{itemize}
        \textbf{Innovation Center of St. Vrain Valley Schools}
        \begin{itemize}
          \vspace{-5pt}
          \item Advanced Cybersecurity with Python Programming, Summer 2023. (Intensive 7-Hour/Day Weeklong Course). Instructor.
          \vspace{-5pt}
          \item Fundamentals of Cybersecurity, Summers 2019-2022. (Intensive 7-Hour/Day Weeklong Course). Instructor.
        \end{itemize}
      
        % \begin{itemize}
        %     \itemsep -1pt {}
        %     \item Sought to understand optimal liquidity provisioning in decentralized exchanges and prediction markets.
        %     \item Sought to understand aspects of liquidity provisioning from a contract design perspective and formulated a general theory for automated market makers, resulting in the paper:
        %     \begin{itemize}
        %       \item \bibentry{bhaskara2023general}
        %     \end{itemize}
        %     \item Developed basic understanding of topics in algorithmic game theory and computational social choice theory.
        %     \item Active in the algorithmic economics reading group.
        % \end{itemize}
      %   \resumeSubheading{University of Colorado Boulder}{Boulder, CO}
      %   {CSCI 3104: Algorithms Learning Assistant}{January, 2024 - May, 2024}
    
      %   \begin{itemize}
      %       \itemsep -1pt {}
      %       \item Met regularly with the Algorithms instructional team to prepare for the upcoming week of instruction and ensure student success.
      %       \item Held regular office hours to help students with fundamental algorithms concepts including graph algorithms, the divide-and-conquer paradigm, dynamic programming, amortized analysis, and computational complexity theory.
      %       \item Served as a resource for students to voice questions and concerns about Calculus I content.
      %   \end{itemize}
      % \resumeSubheading{University of Colorado Boulder}{Boulder, CO}
      %   {MATH 1300: Calculus I Learning Assistant}{January, 2023 - May, 2023}
    
      %   \begin{itemize}
      %       \itemsep -1pt {}
      %       \item Co-led two weekly recitation sections of \(\approx 35\) students each for Calculus I with a graduate teaching assistant.
      %       \item Met regularly with the Calculus I instructional team to prepare for the upcoming week of instruction and ensure student success.
      %       \item Tutored students in the University of Colorado Boulder's Mathematics Academic Resource Center help room.
      %       \item Served as a resource for students to voice questions and concerns about Calculus I content.
      %   \end{itemize}
    %     \resumeSubheading{St. Vrain Valley Schools Innovation Center}{Longmont, CO}
    %     {Founding Member of the Cybersecurity Student Project Team}{August, 2019 - July, 2022}
    
    %     \begin{itemize}
    %         \itemsep -1pt {}
    %         \item Spearheaded effort to create middle school computer programming competition.
    %             \begin{itemize}
    %                 \item Served as competition administrator and lead problem author. Oversaw development of \(\approx 80\) problems.
    %                 \item Fielded \(13\) teams of \(2\) to \(4\) students per team in inaugural year.
    %             \end{itemize}
    %         \item Organized St. Vrain Valley Schools' participation, and competed, in the National CyberPatriot Competition (\(\approx 30\) competitors).
    %             \begin{itemize}
    %                 \item Led practices and presented on topics in Linux system administration.
    %                 \item Led own team to platinum tier of competition and semifinal rounds multiple times.
    %             \end{itemize}
    %         \item Taught introductory cybersecurity classes of \(\approx 25\) students and developed instructional materials; trained coworkers.
    %         \item Regularly presented to district and community leaders, including Governor Jared Polis, during board meetings and Innovation Center tours.
    %     \end{itemize}
     \vspace{-5pt}
        % \resumeSubheading
        % {Silver Creek High School}{Longmont, CO}
        % {Instructional Student Assistant Program Director}{August, 2021 -  May, 2022}
        % \begin{itemize}
        %         \itemsep -1pt {}
        %         \item Served as head teaching assistant.
        %         \item Created lessons and miscellaneous instructional materials, assisted students, and gave lectures for Algebra I, Algebra II, and Introductory Physics.
        %         \item Oversaw \(7\) teaching assistants in Prealgebra, Geometry, Integrated English and History, United States History, and Personal Finance. Led monthly professional development meetings.
        %     \end{itemize}
    
    \vspace{-5pt}
    
    \begin{comment}
    %-----------PROJECTS-----------------
    \vspace{-5pt}
    \section{Projects}
    \resumeSubHeadingListStart
    \resumeSubItem{Vison - multimedia search engine (NLP, Search Engine, Web Crawlers, Multimedia Processing)}{(Work in progress) Research oriented, open source, search engine for bringing reverse multimedia search to small \& mid scale enterprises. Tech: Python, NodeJS, Intel OpenVino Toolkit, Selenium, TensorFlow (October '18)}
    \vspace{2pt}
    \resumeSubItem{Reinforcement Learning based Traffic Control System (Reinforcement Learning, Computer Vision)}{AI model to resolve city traffic around 50\%
    faster. Tech: Python, Alibaba Cloud, Raspberry Pi, Arduino, SUMO \& OpenCV. (August '18)}
    \vspace{2pt}
    \resumeSubItem{Panorama from Satellite Imagery using Distributed Computing (Distributed Computing, Image Processing)}{Images clicked using drones, provided by ISRO were stitched together using distributed public compute nodes, effectively bringing down processing time exponentially. Tech: PHP, C++, Java, Python (March '18)}
    \vspace{2pt}
    \resumeSubItem{Drag-n-drop machine learning learning environment (Web Development, Machine Learning)}{Scratch like tool for implementing machine learning pipelines along with built in tutorial for each concept. Tech: Python, JavaScript (September '18)}
    \vspace{2pt}
    \resumeSubItem{Search Engine and Social Network(Web Development, Web Crawler, Search)}{Created from scratch a social network and a search engine based on the idea of integrating Facebook and Google. The launched website was among top 1000 websites in India during 2012-2013. Tech: PHP, MySQL, HTML, CSS, WebSockets, JavaScript, RSS, XML ( May '12)}
    \resumeSubHeadingListEnd
    \vspace{-5pt}
    \section{Publications}
    \resumeSubHeadingListStart
    \resumeSubItem{Book: Deep Learning on Web (Web Development, Deep Learning)}{Work in Progress book to be published by Packt Publishing in late 2019. Tech: Django, Python, AWS, GCP, Azure (November '18)}
    \vspace{2pt}
    \resumeSubItem{Book: Deep Learning on Mobile Devices (Flutter App Development, Deep Learning)}{Work in Progress book to be published by Packt Publishing in late 2019. Tech: Flutter, Android, Firebase, TensorFlow, Python, Dart (December '18)}
    \resumeSubHeadingListEnd
    \vspace{-5pt}
    %-----------Awards-----------------
    \section{Honors and Awards}
    \begin{description}[font=$\bullet$]
    \item {Awarded title of Intel Software Innovator - May, 2019}
    \vspace{-5pt}
    \item {Second Runner's Up at TCS EngiNx Engineering Project Innovation Content - September, 2018 }
    \vspace{-5pt}
    \item {Runner's Up at Facebook Developers Circle Hackathon - August, 2017}
    
    \end{description}
    
    \vspace{-5pt}
    \section{Volunteer Experience}
      \resumeSubHeadingListStart
      \resumeSubheading
        {Community Lead at Developer Student Clubs NSEC}{Kolkata, India}
        {Conducted online and offline technical \& soft-skills training impacting over 3000 students.}{Jan 2019 - Present}
    \vspace{5pt}
        % \vspace{10pt}\textbf{\large{Community Experience}}
        \resumeSubheading
        {Event Organizer at Google Developers Group Kolkata}{Kolkata, India}
        {Organized events, conducted workshops and delivered workshops reaching over 7000 developers.}{Jan 2018 - Present}
    
    \resumeSubHeadingListEnd
    \end{comment}
    \pagebreak
    \bibliographystyle{plain}
    \bibliography{../resume.bib}
    \end{document}
    